Technical Report

### 2024-03-07 Reports/tech_report1.tex
update report

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.

@@

>>>>

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 47 ReLU.

@@

\section*{March 6}

This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 37 node. The major update is the new formula of finding open ReLU.

The running code's file name is \verb*|DiamondLipschitz_V0p9_test.py|. And the partial output file name is \verb*|DL_V0p9_layer7_open37_c0p5_1.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 37 ReLU.

\begin{itemize}
	\item\emph{Experiments Id}: 030600102024

	\item\emph{Open $\ReLU$ number:} Open 37 ReLU node with coefficient 0.5.

The new feature is that we update the formula of finding open ReLU nodes.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p9_layer7_open37_c0p5_1.txt|.

	\item \emph{Total time:} 34544s.

	\item \emph{Key results:}  The average gamma of this layer is:  2.7242726913878657

	The average solution for gamma of this layer is:  2.521051645492814

	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_06_23_12_22.b|.
